Lyman-$\alpha$ photons through rotating outflows

### 2018-03-31 paper/paper.tex
edit

@@

\subsubsection{\lya Kinematic Maps}
The first is related to the capability of spatially resolving the
extent of a LAE.
For instance \cite{Prescott14} presented observational results of a
Doppler shift when taking spectra at two oposite sides of a LAE.

@@

\subsubsection{\lya continuum escaping or rotation?}

>>>>

\begin{figure}
  \begin{center}
    \includegraphics[width=0.48\textwidth]{./figures/results/muse_vs_simulations.pdf}
  \end{center}
  \caption{\textbf{Comparison between observations and simulations.}  
    \label{fig:muse}}
\end{figure}

@@

\subsubsection{\lya continuum leakage or rotation?}

\subsubsection{\lya Kinematic Maps}

Current observational facilities have the capability of spatially
resolving the extent of a LAE.
For instance \cite{Prescott14} presented observational results of a
Doppler shift when taking spectra at two oposite sides of a LAE.

@@

\subsubsection{Match to \lya observations by MUSE}

In order to give the reader a feeling of the ranges of observational
data that can be explained by the models presented here we perform a
comparison against observational data from MUSE.
